\textbf{COMP0085 Summative Assignment}

### 2023-01-06 submission.tex
fix typo

where $\delta[\textbf{x}]$ are the concentration perturbations, $\epsilon \sim \mathcal{N} (0, \Psi)$ are the reaction specific Gaussian noise variables, \Lambda is the factor loading matrix, and $z \sim \mathcal{N} (0, I)$ are the latent factors, the parent concentration perturbations.

>>>>

where $\delta[\textbf{x}]$ are the concentration perturbations, $\epsilon \sim \mathcal{N} (0, \Psi)$ are the reaction specific Gaussian noise variables, $\Lambda$ is the factor loading matrix, and $z \sim \mathcal{N} (0, I)$ are the latent factors, the parent concentration perturbations.
